\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\begin{document}

% ===== Header =====
\begin{center}
    {\LARGE \textbf{Shahadat Hussain}} \\[4pt]
    Research Associate · Division of Engineering, CTP Lab \\
    New York University, Saadiyat Island, Abu Dhabi, UAE 129188 \\
    +971 50 628 0812 \,|\, \href{mailto:shahadat_ind@yahoo.com}{shahadat\_ind@yahoo.com} \,|\, 
    \href{https://sites.google.com/view/shahadathussain}{Portfolio} \\
    \href{https://linkedin.com/in/shahadathussain}{LinkedIn} \,|\, shah.bksc
\end{center}

\vspace{0.2in}

% ===== Summary =====
\section*{Summary}
An adept researcher with over four years of expertise in 3D printing, actively involved in projects focusing on additive manufacturing. Skilled in fabricating prototypes, advanced materials characterization, mechanical testing, and data analysis/visualization using Python libraries (pandas, numpy, scipy, matplotlib, seaborn). Published multiple scientific articles.

% ===== Work Experience =====
\section*{Work Experience}

\textbf{Research Associate}, Division of Engineering, New York University, Abu Dhabi \hfill \textit{Sep 2024 -- Present}  
\begin{itemize}[leftmargin=*]
    \item Hybrid manufacturing: stereolithography, fused deposition, polyjet, LPBF, robotic arm arc printing, investment casting.
    \item Conducting tensile/fatigue testing and materials characterization (SEM, XRD, EDS, metallography).
    \item Writing review articles on 3D printing applications in civil engineering.
\end{itemize}

\textbf{Postdoctoral Researcher}, Mechanical Engineering, Khalifa University, Abu Dhabi \hfill \textit{Feb 2020 -- Jun 2024}  
\begin{itemize}[leftmargin=*]
    \item Analyzed attributes of NiTi TPMS structures (Schwartz primitive, Schoen gyroid lattices).
    \item Conducted tensile/fatigue tests and characterizations with SEM, XRD, EDS, metallography.
    \item Published 5 research papers; developed lab manuals.
\end{itemize}

\textbf{Project Fellow}, CSIR-AMPRI, Bhopal, India \hfill \textit{May 2013 -- Aug 2014}  
\begin{itemize}[leftmargin=*]
    \item Performed alloy synthesis, metallography, heat treatment, and characterization (spectroscopy, microscopy, calorimetry).
    \item Published 2 research papers, presented at national conferences, collaborated with IIT Madras.
\end{itemize}

% ===== Education =====
\section*{Education}

\textbf{Ph.D. in Materials Science and Technology}, AcSIR, Bhopal, India \hfill \textit{Aug 2014 -- Jun 2019}  
- Research on Cu–Al–Ni shape memory alloys. Published 2 papers, 5 conference presentations.

\textbf{B.E. in Mechanical Engineering}, UIT-RGPV, Bhopal, India \hfill \textit{Aug 2008 -- May 2012}  
- Graduated First Division. Industrial training at SAIL Bokaro.

% ===== Skills =====
\section*{Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Software:} FreeCAD, Python (pandas, numpy, matplotlib, seaborn), Origin, ImageJ, LaTeX.
    \item \textbf{Fabrication:} Additive manufacturing, vacuum induction melting, heat treatment.
    \item \textbf{Testing:} Tensile, compression, fatigue (Instron 5969, 8872).
    \item \textbf{Characterization:} SEM (JEOL 7610F, FEI Nova, Quanta 3D FIB), XRD, DSC, optical microscopy.
\end{itemize}

% ===== Projects =====
\section*{Projects}

\textbf{Additive Manufacturing of NiTi Shape Memory Alloys}, Khalifa University, Abu Dhabi \hfill \textit{Feb 2020 -- Present}  
- 3D printing NiTi TPMS structures; performed SEM, TEM, XRD, AFM, DSC, fatigue tests.  
- Published 5 research articles, conference presentations, developed lab manuals.  

\textbf{Design and Development of Thermo-Responsive and Magnetic Shape Memory Materials}, CSIR-AMPRI, Bhopal \hfill \textit{Jun 2013 -- Aug 2014}  
- Developed Cu-based shape memory materials with high transition temperatures.  
- Published 2 articles, national presentations, IIT Madras collaboration.  

% ===== Certifications =====
\section*{Certifications}
- IBM: Introduction to Project Management (2024)  
- Arizona State University: Additive Manufacturing Specialization (2024)  
- IBM: Data Science Professional Certificate (2024)  
- University of Michigan: Python for Everybody (2024)  
- Udemy: FreeCAD Basic 3D Modeling (2023)  

% ===== Publications =====
\section*{Publications}
- Hussain, S., Alagha, A. N., Zaki, W. (2024). Phase Transformation Behavior of NiTi TPMS Lattices Fabricated by LPBF. \textit{Journal of Materials Engineering and Performance}. \href{https://doi.org/10.1007/s11665-024-09162-7}{DOI}.  
- Hussain, S., Alagha, A. N., Haidemenopoulos, G. N., Zaki, W. (2023). Microstructural and Surface Analysis of NiTi TPMS Sections by LPBF. \textit{Journal of Manufacturing Processes}, 102:375–386. \href{https://doi.org/10.1016/j.jmapro.2023.07.055}{DOI}.  

\end{document}
